\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-20 doc/acknowledgments.tex
Fixed fuzziness of crowd plots by switching to PDF format. #127

We thank all \Ncollaboration members of the \sw community for their
contributions to the project so far. A complete list of collaborators is
provided at \texttt{http://spacewarps.org/\#/results/CFHTLS}.

>>>>

We thank all 36,982 members of the \sw community for their
contributions to the project so far. A complete list of registered
collaborators is provided at \texttt{http://spacewarps.org/\#/results/CFHTLS}.
